Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
analyze stand features and create output

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Read and prepare data 
```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
compara <- function(df, mivariable){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest

@@

  return(output)
}  
```

@@

# Select only variables to compare 
compe_sel <- compe %>% dplyr::select(ba:dnn,site)
# Get vector with variables 
variables <- compe %>% dplyr::select(ba:dnn) %>% names()

@@

ala <- xxx(df=topo, mivariable='slope')

# Get table 
mymult <- as.data.frame(table_glht(tuk))

  mymult <-

  aux <- 
pander(aov_dnn$mymult, round=4,caption = "Post hoc comparison (Tukey, alpha = 0.05)", missing = '', 
     emphasize.strong.cells = 
             which(aov_ba$mymult < 0.05 & aov_ba$mymult == aov_ba$mymult[,4], arr.ind = T))

aov_ba$mymult

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output:  
  md_document:
    toc: true
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Read and prepare data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

#### Function to comparison (aov)
```{r}
compara <- function(df, mivariable){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest

@@

  # Return also summary values 
  summ_values <- df %>% 
    dplyr::select_(mivariable, 'site') %>%
    group_by(site) %>% 
    summarise_each(funs(mean, sd, se=sd(.)/sqrt(n())))

  # Join letters and summary values
  output$summ_values <- summ_values

  summ_comparison <- summ_values %>% left_join(df_letter, by='site')

  output$summ_comparison <- summ_comparison

  return(output)
}

## Comparison

@@

# Select only variables to compare 
compe_sel <- compe %>% dplyr::select(ba:dnn,site)

# Get vector with variables 
variables <- compe %>% dplyr::select(ba:dnn) %>% names()

@@

# Loop to export into txt files (see ./out/anovas_competition ... )
for (i in variables){

  out <- get(paste0('aov_', i))

  sink(paste0(di,'out/anovas_competition/aov_', i, '.txt'))
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

  cat("MODEL pretty \n")
  print(out$tm) 
  cat("\n")

  cat("POST HOC \n")
  print(out$mymult) 
  cat("\n")

  cat("SUMMARY VALUES \n")
  print(out$summ_comparison) 
  cat("\n")

  sink()
}
```

## Distance-Independet Indices 
### Basal Area
```{r}
mivariable <- 'ba'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Stand Density
```{r}
mivariable <- 'std'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Plot Density
```{r}
mivariable <- 'pd'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Number of competitors within *r* meters (10 m)
```{r}
mivariable <- 'n_competitors'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Number of competitors within *r* meters (10 m) such that $ dbh_j > dbh_i $
```{r}
mivariable <- 'n_competitors_higher'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Sum of size of trees within *r* meters (10 m)

```{r}
mivariable <- 'sum_sizes'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

## Size ratio

```{r}
mivariable <- 'sr'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

## Distance-Dependet Indices

### Distance to nearest tree       
```{r}
mivariable <- 'dnn'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Crowding       
```{r}
mivariable <- 'crowding'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Lorimer

```{r}
mivariable <- 'lorimer'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Negative Exponential size ratio

```{r}
mivariable <- 'nesr'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Negative Exponential Weighted size ratio
```{r}
mivariable <- 'newsr'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Size ratio proportional to distance

```{r}
mivariable <- 'srd'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```

### Size difference proportional to distance

```{r}
mivariable <- 'sdd'
s <- get(paste0('aov_', mivariable))

s$summ_comparison %>% 
  pander(round=4, caption=paste0('Mean values (', mivariable,')'))

tm <- s$tm

pander(tm, round=5,
       caption=paste0('ANOVA table (', mivariable,')'), 
       missing = '', emphasize.strong.cells = 
               which(tm < 0.1 & tm == tm$p.value, arr.ind = T))
```
